---
title: "Projects reproducible"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
#Abstract
A reproduction of the analysis for Experiment 2 in Mehr, Song, and Spelke (2016).
#Introduction
 This report's goal is to reproduce the analysis of Experiment 2 in Mehr, Song, and Spelke (2016). The citation for this article is Mehr, S. A., Song. L. A., & Spelke, E. S. (2016). For 5-month-old infants, melodies are social. Psychological Science, 27, 486-501.
 The data was downloaded https://osf.io/y3kzd. The experiment involved one sample t-test and a paired T-test. The experiment involved testing the reaction of the times the infants looked at and noticed a familiar song coming out of a inanimate object.
 
#Methods 

##Patricipants
There were 32 full-term infants that were included in the final analysis of this experiment.

##Procedure
 The infants were exposed to a recording of a song through a musical toy and then were tested using a selective-attention test.

```{r}
## Results
library(data.table)
all_data <- read.csv("Projectdata/LUL_pss.csv")

library(dplyr)
experiment_one <- all_data %>% filter(exp2==1)

t.test(experiment_one$pref1, mu=.5)
##One Sample t-test
t.test(experiment_one$pref2, mu=.5)

#Paired T-test
t.test(experiment_one$pref1,experiment_one$pref2, paired=TRUE, var.equal=TRUE)

difference_scores <- experiment_one$pref1-experiment_one$pref2
length(difference_scores[difference_scores>0])

Phase <- rep(c("Baseline","Test"), each = 32)
Proportions <- c(experiment_one$pref1,experiment_one$pref2)
plot_df <- data.frame(Phase,Proportions)

#Reproducing the figure
library(ggplot2)
ggplot(plot_df, aes(x=Phase, y=Proportions))+
  geom_point()
mean_df <- aggregate(Proportions ~ Phase, plot_df, mean)

ggplot(plot_df, aes(x=Phase, y=Proportions))+ 
  geom_point()+
  geom_point(data=mean_df, color="Red", size=2)
ggplot(plot_df, aes(x=Phase, y=Proportions))+ 
  geom_point()+
  geom_bar(data=mean_df, stat="identity",aes(fill=Phase))
difference_scores <- experiment_one$pref1-experiment_one$pref2 #calculate difference scores
standard_error <- sd(difference_scores)/sqrt(length(difference_scores)) #calculate SEM


ggplot(plot_df, aes(x=Phase, y=Proportions))+ 
  geom_bar(data=mean_df, stat="identity",aes(fill=Phase))+
  geom_errorbar(data=mean_df, aes(ymin=Proportions-standard_error, 
                                  ymax=Proportions+standard_error), width=.1) +
  geom_point(alpha=.25)
```
#Results
In the attention test it was found that the infants looked equally at the two unfamiliar adults during the baseline .5; M = .512, SD = .175, 95% CI = [.449, .575]), t(31) = 0.39,p = .70. In the paired t-test it was shown that the infants attention was similar to the baseline of experiment 1. M = 15.2 s, SD = 6.69), t(31) = 0.95, p = .35

#Discussion 
The re-analysis successfully reproduced the analysis reported by Mehr, Song, and Spelke (2016). 

## Simulation-based power analysis
```{r}
library(pwr)
pwr.t.test(n=32, d=.2,type="two.sample", alternative="two.sided")
```
```{r}
A <- rnorm(n=32,mean=16.2, sd=5.18)
B <- rnorm(n=32,mean=15.2, sd=6.69)
t.test(A,B,var.equal=TRUE)$p.value
sim_null <- function(){
  A <- rnorm(n=32,mean=16.2, sd=5.18)
B <- rnorm(n=32,mean=15.2, sd=6.69)
 return(t.test(A,B,var.equal=TRUE)$p.value)
}
outcomes <- replicate(1000,sim_null())






effect_sizes <- c(.05,.1,.2)
power <- sapply(experiment_one$pref1, 
          FUN = function(x) {
            pwr.t.test(n=32,
            d=x,
            sig.level=.05,
            type="two.sample",
            alternative="two.sided")$power})
library(ggplot2)
ggplot(plot_df, aes(x=effect_sizes,
                    y=power, fill = experiment_one$pref1 ))+
  geom_line()+
  geom_point()
  
```
# References
Mehr, S. A., Song. L. A., & Spelke, E. S. (2016).
